SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-13 docs/questioning.tex
conclusions draft ready

\author{
\IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
Panos Louridas,\IEEEauthorrefmark{2}
Michalis Polychronakis,\IEEEauthorrefmark{1}
and Angelos D. Keromytis\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}
Network Security Lab\\
Department of Computer Scinence\\
Columbia University\\
\{dimitro, mikepo, angelos\}@cs.columbia.edu\\
\IEEEauthorrefmark{2}
Software Engineering and Security Lab\\
Department of Management Science and Technology\\
Athens University of Economics and Business\\
louridas@aueb.gr
}}

@@

Despite many approaches that have been developed,
application attacks based on source code injection
have been consistently present for the last 15 years,
and it appears that they will continue to be.
Attackers seem to find new ways to introduce
source code to applications by using a variety of
languages and techniques~\cite{HNSHS12,DKH14}.
Meanwhile, during the last decade, there are
numerous mechanisms that have been developed to
detect one or more of such attacks. However,
% even if
% some of them share characteristics with supported frameworks
% like Mozilla's Content Security
% Policy\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}
% ({\sc csp}) and Google
% Caja\footnote{\url{https://code.google.com/p/google-caja/}}~\cite{M06},
the majority of them are not used in practice.

In our research we tried to identify some of the reasons
why this is the case. Some of these reasons include
poor testing, high overhead, code unavailability,
deployment and security issues. However, our
systematization suggests that there are many
promising cases. For instance there are
many mechanisms that seem to have been extensively
tested in terms of accuracy ({\sc sqlc}eck, {\sc amnesia},
{\sc dsi}, libAnomaly), solve specific
problems in an efficient way (Blueprint and the system
by Stock et al.) or have a low computational overhead
({\sc dsi} and the system by Phung et al.).
There are also cases that researchers have made their
code available ({\sc beep} and {\sc sd}river) which
can be a push towards the development of better mechanisms.
Apart from making the source code of such mechanisms
available, we also believe that testing them in
a production setting could propel their adoption.

>>>>

% \author{
% \IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
% Panos Louridas,\IEEEauthorrefmark{2}
% Michalis Polychronakis,\IEEEauthorrefmark{1}
% and Angelos D. Keromytis\IEEEauthorrefmark{1}}
% \IEEEauthorblockA{\IEEEauthorrefmark{1}
% Network Security Lab\\
% Department of Computer Scinence\\
% Columbia University\\
% \{dimitro, mikepo, angelos\}@cs.columbia.edu\\
% \IEEEauthorrefmark{2}
% Software Engineering and Security Lab\\
% Department of Management Science and Technology\\
% Athens University of Economics and Business\\
% louridas@aueb.gr
% }}

\author{Anonymous Submission}

@@

Despite many approaches that have been developed,
application attacks based on source code injection
have been consistently present for the last 15 years,
and it appears that they will continue to be.
Attackers seem to find new ways to introduce
source code to applications by using a variety of
languages and techniques~\cite{HNSHS12,DKH14}.
Meanwhile, during the last decade, there are
numerous mechanisms that have been developed to
detect one or more of such attacks. However,
even if some of them share characteristics
(for instance, {\sc html} sanitization and {\tt eval} handling)
with supported frameworks like Mozilla's Content Security
Policy\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}
({\sc csp}) and Google
Caja\footnote{\url{https://code.google.com/p/google-caja/}}~\cite{M06}
the majority of them are not used in practice.

In our research we tried to identify some of the reasons
why this is the case. Some of these reasons include
poor testing, high overhead, code unavailability,
deployment and security issues. However, our
systematization suggests that there are many
promising cases. For instance there are
mechanisms that have been extensively
tested in terms of accuracy ({\sc sqlc}heck, {\sc amnesia},
{\sc dsi}, libAnomaly), solve specific
problems in an efficient way (Blueprint and the system
by Stock et al.) or have a low computational overhead
({\sc dsi} and the system by Phung et al.).
There are also cases that researchers have made their
code available ({\sc beep} and {\sc sd}river) which
can be a push towards the development of better
mechanisms. This argument has been raised
by another {\sc s}o{\sc k} paper too~\cite{SPWS13}.
We believe that testing defenses in
a production setting could also propel their adoption.

We hope that the exploitation model, analysis
and observations that emerged from our research
can be a reference point for researcher who
wish to develop new countermeasures that
detect web application attacks.
